---
title: "assignment_1_trial_2"
author: "Jessie Lilly"
date: "February 21, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. First load tidyverse and lubridate. 

```{r}
library(tidyverse)
library(lubridate)
```
## 2. Upload data file



```{r}
blpw.all <- readRDS("~/RM11/assignment_2/blpw.all.RDS")

```

## 3. Check the status of each column

```{r}
sapply(blpw.all, class)
```

## Change year and month to be integers. 

```{r}
blpw.all$year<-as.integer(blpw.all$year)
blpw.all$month<-as.integer(blpw.all$month)

```
## Combine the year,month, and day into one column. 

```{r}
blpw.all$date<-with(blpw.all, ymd(paste(year,month,day,sep = "-")))

```

## Create a table that is grouped by band and date, then take the first measure of mass, and subtract it from the next measured mass 

```{r}
blpw.band <- blpw.all %>%
  group_by(band) %>%
  arrange(band,date) %>%
  mutate(diff_mass=mass-first(mass)) %>% data.frame()
```
 ##Changell 0 values to NA, Remove all birds where change in mass is equal to 0 (NA)
```{r}
data.filtered <- blpw.band[blpw.band==0]<-NA
data.filtered<- na.omit(blpw.band)
```



##Graph the change in Mass for all recaptured birds.

```{r}
ggplot(data=data.filtered,mapping=aes(x=month,y=diff_mass,colour=band))+
+ geom_point()+
+ geom_line()+
+ facet_wrap(~location,nrow=1)+
+ theme(legend.position='none')